Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-07-28 Documents/Paper/ms.tex
Some refs

%\section{``Transit'' Example}
%\section{``Asteroseismology'' Example}
\section{``Galaxy Field'' Example}

@@

\begin{thebibliography}{}

@@

\bibitem[Brewer et al.(2013)]{2013AJ....146....7B} Brewer, B.~J., 
Foreman-Mackey, D., Hogg, D.~W.\ 2013.\ Probabilistic Catalogs for Crowded 
Stellar Fields.\ The Astronomical Journal 146, 7.

@@

@@

>>>>

%\section{``Transit'' Example}
%\section{``Asteroseismology'' Example}
\section{``Galaxy Field'' Example}
Source detection is an important problem in astrophysics. Given some data,
usually one or more noisy, blurred, images of the sky, we would like to know
how many objects $N$ (such as stars or galaxies) are in the image, and their
properties (such as flux, size, orientation). Various ad-hoc approaches exist,
covering a wide spectrum between ad-hoc approaches and principled inference
approaches
\citep[e.g.][]{irwin, sextractor, dolphot, 2003MNRAS.338..765H, starfield}.

In this section we apply
the DNS approach to a toy version of the problem of detecting and quantifying
extended objects such as galaxies in a noisy image.

@@

\begin{thebibliography}{}
\bibitem[Bertin and
Arnouts(1996)]{sextractor} Bertin, E., Arnouts, S.\ 1996.\ SExtractor: Software for source extraction.\ Astronomy and Astrophysics Supplement Series 117, 393-404.

@@

\bibitem[Brewer et al.(2013)]{starfield} Brewer, B.~J., 
Foreman-Mackey, D., Hogg, D.~W.\ 2013.\ Probabilistic Catalogs for Crowded 
Stellar Fields.\ The Astronomical Journal 146, 7.

@@

\bibitem[Dolphin(2000)]{dolphot} Dolphin, A.~E.\ 2000, PASP, 
112, 1383

@@

\bibitem[Hobson 
\& McLachlan(2003)]{2003MNRAS.338..765H} Hobson, M.~P., \& McLachlan, C.\ 2003, \mnras, 338, 765

\bibitem[Irwin(1985)]{irwin} Irwin, M.~J.\ 1985, \mnras, 214,
575
